---
title: "Untitled"
output:
  html_document: default
  pdf_document: default
date: "2024-01-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Escribir texto

```{r}
x <- 5
x
```

$$
\frac{x}{n}
$$
# Including Plots
## Including Plots
### Including Plots
#### Including Plots
##### Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


# R

```{r}
x <- 5
x
```

Datos atómicos

```{r}
5
"asdas"
TRUE
5.7
```

Estructuras de datos

```{r}
c(3, 4, 5, 6, 7)
```

Promoción y casteo

```{r}
v <- c("1", 3, 4)
```

```{r}
l <- list(3, 4, 5, "asa", list(2, 3, 5))
```

```{r}
matrix(c(v, v, v), nrow = 3)
```
```{r}
data.frame(l)
```
```{r}
factor(v)
```

```{r}
factor(v, ordered = TRUE)
```

ciclos: 

+ For
+ While
+ Do-while

```{r}
for(i in seq(1, 10, 2)){
  print(i)
}
```
```{r}
flag <- TRUE
i <- 0
while(flag){
  print(i)
  i = i + 1
  print("Ya sumé")
  if(i == 11){
    print("Entro el if")
    flag <- FALSE
  }
}
```
```{r}
integer(34)
```

```{r}
as.integer(v)
```

```{r}
?rnorm()
```

Establecemos una semilla

```{r}
x1 <- rnorm(42)
x2 <- rnorm(42) + rnorm(42)
```

```{r}
plot(x1, x2)
```


```{r}
library(tidyverse)

tibble(x1,x2) %>% 
  ggplot(aes(x = x1, y = x2)) + 
  geom_point() + 
  theme_minimal() + 
  ggtitle("X vs Y") + theme(axis.text.x = element_text(angle = 45),
    panel.background = element_rect(linetype = "dashed"),
    plot.background = element_rect(fill = "antiquewhite"))
```

En el código anterior hicimos uso del addin ggplot Theme Assistant. Pueden encontrar información [aquí](https://github.com/calligross/ggthemeassist) y para su instalación pueden ejecutar el siguiente código

```{r eval=FALSE, include=TRUE}
install.packages("ggThemeAssist")
```

